\input{./lib/hw-setup/tex/HWSetup}
\input{./lib/hw-setup/tex/EngBindings}

%
% Homework Details
%   - Title
%   - Subtitle
%   - Due date
%   - Due time
%   - Course
%   - Section/Time
%   - Instructor
%   - Author
%

\hwkTitle{HW02}
\hwkSubTitle{Propulsive Glide Travel from Clavius to Tycho}
\hwkDueDate{2026-02-27}
\hwkDueTime{11:59:00}
\hwkClass{ENAE488X - 0101}
\hwkClassTime{17:00:00}
\hwkInstructor{Dr. Akin}
\hwkAuthor{Vai Srivastava}
\hwkCompletionDate{\today}

\begin{document}

\maketitle

\pagebreak

\section*{Overview} \label{sec:overview}

In the \textit{2001: A Space Odyssey} video clip of propulsive glide shown in \href{https://github.com/vaisriv/uni/blob/main/26s/ENAE488X/docs/lectures/lec02.pdf}{Lecture \# 2}, the vehicle was traveling from Clavius to Tycho, a distance of \qty{470}{\km}. For the time being, assume both departure and destination are at the same elevation, that the Moon is essentially flat, and that the propulsion systems use \ce{LOX}/\ce{LH2} propellants with an exhaust velocity \( v_{e} = \qty{4500}{\m\per\s} \). Lunar gravity is \qty{1.622}{\m\per\s\squared}.

\begin{hwkProblem*}{1}{} \label{hwk:p01}

	Assuming this mission was an optimum propulsive glide,
	\begin{enumerate}[label=\alph*.]
		\item \label{hwk:p01a} What horizontal velocity would the vehicle have?
		\item \label{hwk:p01b} How long would the flight take (in minutes)?
		\item \label{hwk:p01c} What would the total \( \Delta v \) be for this trip?
		\item \label{hwk:p01d} If the vehicle has an empty mass of \qty{4000}{\kg}, how much propellant would be required for this trip?
	\end{enumerate}

	\hwkSol{} \label{hwk:s01}

	\hwkPart{} \label{hwk:s01a}

	Answer

	\hwkPart{} \label{hwk:s01b}

	Answer

	\hwkPart{} \label{hwk:s01c}

	Answer

	\hwkPart{} \label{hwk:s01d}

	Answer

\end{hwkProblem*}

\begin{hwkProblem*}{2}{} \label{hwk:p02}

	If the vehicle made the trip using a single ballistic hop,
	\begin{enumerate}[label=\alph*.]
		\item \label{hwk:p02a} What \( \Delta v \) would be required for the initial launch?
		\item \label{hwk:p02b} How long would the flight take (in minutes)?
		\item \label{hwk:p02c} What would be the maximum height the vehicle reaches between departure and destination?
		\item \label{hwk:p02d} What is the total \( \Delta v \) for this trip?
		\item \label{hwk:p02e} If the vehicle has an empty mass of \qty{4000}{\kg}, how much propellant would be required for this trip?
	\end{enumerate}

	\hwkSol{} \label{hwk:s02}

	\hwkPart{} \label{hwk:s02a}

	Answer

	\hwkPart{} \label{hwk:s02b}

	Answer

	\hwkPart{} \label{hwk:s02c}

	Answer

	\hwkPart{} \label{hwk:s02d}

	Answer

	\hwkPart{} \label{hwk:s02e}

	Answer

\end{hwkProblem*}

\begin{hwkProblem*}{3}{} \label{hwk:p03}

	The Moon is actually a sphere with a radius of \qty{1738}{\km}. Repeat the analysis of \hyperref[hwk:p01]{Problem 1} assuming a spherical planet instead of a flat one.
	\begin{enumerate}[label=\alph*.]
		\item \label{hwk:p03a} What horizontal velocity would the vehicle have?
		\item \label{hwk:p03b} How long would the flight take (in minutes)?
		\item \label{hwk:p03c} What would the total \( \Delta v \) be for this trip?
		\item \label{hwk:p03d} If the vehicle has an empty mass of \qty{4000}{\kg}, how much propellant would be required for this trip?
	\end{enumerate}

	\hwkSol{} \label{hwk:s03}

	\hwkPart{} \label{hwk:s03a}

	Answer

	\hwkPart{} \label{hwk:s03b}

	Answer

	\hwkPart{} \label{hwk:s03c}

	Answer

	\hwkPart{} \label{hwk:s03d}

	Answer

\end{hwkProblem*}

\begin{hwkProblem*}{4}{} \label{hwk:p04}

	A Mars aircraft uses a jet engine which burns \ce{CO2} of the atmosphere with \ce{H2} fuel carried onboard. This combination has a specific fuel consumption of \qty{9.9e-5}{\per\s}. Since hydrogen is very low density, only 10 \% of the aircraft's weight at takeoff is fuel. It has an \( L/D \) of 20 and files at \qty{200}{\m\per\s}. The gravity on Mars is \qty{3.721}{\m\per\s\squared}. Calculate the range of the aircraft.

	\hwkSol{} \label{hwk:s04}

	Answer

\end{hwkProblem*}

\end{document}
